\documentclass[a4paper, twoside, openright]{book}

\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm, centering]{geometry}

\usepackage[american]{babel}

\usepackage[bibstyle=authoryear, citestyle=apa, dashed=false, backend=biber, block=space, language=english]{biblatex}
\usepackage{csquotes}

\addbibresource{bibliography.bib}

\usepackage{graphicx}

\usepackage{subcaption}

\usepackage{hyperref}

\usepackage{titlesec}

\usepackage{fancyhdr}

\usepackage{emptypage}

\usepackage{amsmath}

\usepackage{float}

\usepackage{ragged2e}

\usepackage{pdfpages}

\usepackage[toc]{appendix}

\linespread{1.5}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\titleformat{\chapter}
{\normalfont\huge\bfseries}{\thechapter.}{0.5em}{\huge}

\titlespacing*{\chapter}{0pt}{-40pt}{25pt}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{\normalsize}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\pagestyle{fancy}
\fancyhf{}
\lhead{\leftmark}
\fancyfoot[R]{\textbf{\thepage}}
\renewcommand{\headrulewidth}{0.4pt} 
\renewcommand{\footrulewidth}{0.4pt}
\setlength{\headheight}{15pt}

\fancypagestyle{plain}{
  \fancyfoot[R]{\textbf{\thepage}}
  \fancyhead{}
  \renewcommand{\headrulewidth}{0pt}
}

\hypersetup{
    colorlinks,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black
}

%--------------------------------
\begin{document}

\input{Cover}

\cleardoublepage
\newpage 
\thispagestyle{empty}
\begin{flushleft}
  \vspace*{15em}
  \justify
  \textbf{Abstract}: The brain dynamics underlying sensorimotor synchronization constitute a complex combination of different neural processes. Here we wanted to investigate the contribution of cortical cortex on rhythmic sensorimotor synchronization when coupling with auditory and visual inputs related to walking movement. The study has a mixed-models study design with auditory (footsteps sound) and visual (point-light figure) inputs set at the frequency rate of 2 Hz. They were used in three different blocks: audio, audiovisual and visual. The study was conducted by means of electroencephalography (EEG) in a frequency-tagging approach on two distinct groups of individuals: healthy control subjects (\textit{N = 21}) and patients with a stroke (\textit{N = 21}). The results of both population groups showed neural responses of the sensorimotor area in all the stimuli presented in a rhythmic condition, though not in the random one. Such outcome is sustained by behavioral questions on the positive feeling towards the distinct stimuli, which appeared with significantly higher values for the inputs repeated in the rhythmic condition. Moreover, sensorimotor synchronization appeared in auditory and audiovisual inputs, but not in the visual one. In the stroke population the neural response patterns resulted weaker than in the control group, and left-lateralized. These results demonstrate that the sensorimotor synchronization can be elicited only by sensory stimuli repeated in a rhythmic sequence and that auditory inputs appear better to induce neural entrainment. Furthermore, it could be concluded that stroke patients preserved the ability of sensory integration and neural entrainment, even if it results reduced compared to healthy individuals. 
  \vspace*{3em}
  \justify
  \textbf{Keywords}: EEG, Frequency-tagging, Stroke, Sensorimotor integration
\end{flushleft}

\tableofcontents

\input{Chapters/Acknowledgements.tex}

\input{Chapters/Introduction.tex}

\input{Chapters/Methodology.tex}

\input{Chapters/Results.tex}

\input{Chapters/Discussion.tex}

\input{Chapters/Conclusion.tex}

\begin{appendices}
  \fancyhead[L]{APPENDICES}
\input{Chapters/Appendix.tex}
\end{appendices}

\printbibliography[heading=bibintoc]

\end{document}